\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineer}
    {Samsung R\&D Institute India-Bangalore}
    {Bangalore, India}
    {July. 2015 - July. 2016}
    {
      \begin{cvitems}
        \item {Worked on Server side programming and designed the service architecture as a part of Internet of Things and Smart Assistant Team for the Jifical application(available on Play Store).}
        \item {Implemented MVC design pattern for the server on AWS using different frameworks like Spring MVC, Hibernate, Java, Cassandra, Machine Learning and Natural Language Processing.}
        \item {Wrote Unit Test cases and Integration Test cases for the application written using JUnit and JMeter.}
        \item{Filed a \textbf{Patent} Application on Multi-touch gestures for applications on devices with curved edge displays.}
        \item{Obtained \textbf{Most Promising Idea Award} during intra division Hackathon.}
      \end{cvitems}
    }
  \cventry
    {Student Trainee Intern}
    {Samsung R\&D Institute India-Bangalore}
    {Bangalore, India}
    {May. 2014 - July. 2014}
    {
      \begin{cvitems}
        \item {Designed and developed an Android based testing application to check the accuracy and correctness of the application's output.}
        \item {Involved different APIs and frameworks based on Android platform and Java.}
        \item{Automated testing using the designed application and measured the accuracy of the details provided by the applications being tested.}
      \end{cvitems}
    }

      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    
\end{cventries}
