\cvsection{Projects}
\begin{cventries}
%\cventry
 %  {Academic Project in Artificial Intelligence.}
  %  {Game Intelligence Using Adversarial Search}
   % {Los Angeles, California}
    %{September 2016}
    %{
     % \begin{cvitems}
      %  \item {Implemented a project on Game Intelligence Using Adversarial Search.}
       % \item{Involved skills in Java, Recursions, Pruning and Search Algorithms.}
      %\end{cvitems}
    %}
  \cventry
    {Researcher for Energy Efficient Image Compression in Multimedia Wireless Sensor Networks under the guidance of Dr. Geetha V}
    {Undergraduate Research, Web Technology and Wireless Sensor Networks}
    {Surathkal, India}
    {July. 2014 - May. 2015}
    {
      \begin{cvitems}
        \item {Researched on enhancing overall lifetime of the network based on the technique of Region of Interest and scheduling.}
        \item{Compared and Enhanced the energy utilisation of the existing compression techniques like SPIHT, JPEG 2000 and JPEG XR.}
        \item {Implemented prototype to compress and transmit image data from remote location with minimal consumption of energy using Matlab, C, ns2.}
        \item{Enhanced the overall lifetime of the entire network by 30\%.}
      \end{cvitems} 
    }
    \cventry
    {Researcher for Web Service Discovery under the guidance of Dr. Sowmya Kamath}
    {Web Service Discovery and Recommendation}
    {Surathkal, India}
    {July. 2014 - May. 2015}
    {
      \begin{cvitems}
        \item {Designed and implemented Web Service Discovery and Recommendation to the user.}
        \item{Involved skills on Machine Learning and Natural Language Processing using Python and MongoDB.}
        \item {Enhanced the efficiency and correctness based on clustering and classification of web services.}
      \end{cvitems} 
    }
  \cventry
    {Researcher for Data Mining and Information Retrieval under the guidance of Dr. Sowmya Kamath}
    {A Graph Based Technique to Find Common News Contents From Multiple News Sources}
    {Surathkal, India}
    {January. 2014 - April. 2014}
    {
      \begin{cvitems}
        \item {Designed and implemented a graph based algorithm to find the common news contents.}
        \item{Involved skills on Natural Language Processing, Machine Learning and Data Mining using Java, MySql and web crawlers.}
        \item{Improved the correctness of the results using graph based techniques.}
        \item{Enhanced and proposed a new method to find common news contents from different sources.}
      \end{cvitems}
    }
    
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}

\end{cventries}
